% =====================================================================
% Throughput Results — focused write-up of the sweep data
% =====================================================================
% Drop-in subsection covering ONLY the empirical results of the
% throughput sweep. Pair with Figure fig_throughput_sweep and
% Table tbl:throughput.
% =====================================================================

\subsubsection{Results}
\label{sec:throughput-results}

Table~\ref{tbl:throughput} and Figure~\ref{fig:throughput-sweep}
report the full sweep. Three operating regimes emerge clearly:

\paragraph{Sustained regime (50--100~req/s)} The pipeline delivered
every flow record at both 50 and 100~req/s. Notably, p50 latency at
100~req/s (144~ms) was \emph{lower} than at 50~req/s (157~ms): with a
fixed 100~ms Spark micro-batch trigger, a higher offered rate fills
each batch with more records and amortises the per-trigger overhead
over a larger payload. p99 latency at 100~req/s was 256~ms, well
within hot-path budgets. Sustained at 100~req/s, this corresponds
to roughly $8.6$~million flows~per~tenant~per~day, which matches the
production target of small-to-medium enterprise tenants.

\paragraph{Saturation regime (200~req/s)} Delivery remained at
100\,\%, but latency increased by an order of magnitude
(p50~$=$~3.14~s, p99~$=$~6.34~s). At this rate the detector consumer
no longer drained each Spark micro-batch within one trigger interval;
work accumulated in the Kafka backlog and the queue length grew
faster than it could be processed. The pipeline still serviced every
record but its real-time guarantee broke down. We label this the
saturation point because a small further increase in offered load
collapses delivery rather than further inflating latency.

\paragraph{Overload regime ($\geq$500~req/s)} At 500~req/s only
23\,\% of records were delivered; at 1000~req/s the figure fell to
15\,\%. The collapse is a positive-feedback effect of Kafka backlog:
once the consumer cannot keep up, in-flight records age out their
detector deadline and the load harness reports them as undelivered
even though they were accepted by the gateway. Latency for the
records that did complete exceeded ten minutes (p99
$\approx$10~min at 500~req/s, $\approx$9~min at 1000~req/s), making
those numbers unrepresentative of any real-time SLA.

\paragraph{Headline} The single-node Spark-augmented architecture
sustains 100~req/s at production-grade latency
(p50~$=$~144~ms, p99~$=$~256~ms, 100\,\% delivery). The saturation
ceiling is approximately 300~req/s on this hardware. Higher
throughput requires either (i) horizontal scale-out via Spark
cluster mode, or (ii) increasing the Spark micro-batch trigger
interval to better match the offered rate—both of which are
deployment-time configurations rather than architectural changes.
